|

### 2023-04-11 paper/00-main.Rmd
created data section
added more figures

---
title: |
  | Bearing the Strain: Analyzing Pass Rush in American Football with Player Tracking Data

@@

authors: 
- name: Quang Nguyen
  thanks: Corresponding author's email
  affiliation: |
    | Department of Statistics & Data Science
    | Carnegie Mellon University
- name: Ronald Yurko
  affiliation: |
    | Department of Statistics & Data Science
    | Carnegie Mellon University
- name: Gregory J. Matthews
  affiliation: |
    | Department of Mathematics and Statistics
    | Loyola University Chicago

@@

```{r child = "02-methods.Rmd"}
```

```{r child = "03-results.Rmd"}
```

```{r child = "04-discussion.Rmd"}
```

>>>>

---
title: |
  | Bearing the STRAIN: Analyzing Pass Rush in American Football with Player Tracking Data

@@

authors: 
- name: Quang Nguyen
  # thanks: Corresponding author's email
  affiliation: |
    | Department of Statistics & Data Science
    | Carnegie Mellon University
- name: Ronald Yurko
  affiliation: |
    | Department of Statistics & Data Science
    | Carnegie Mellon University
- name: Gregory J. Matthews
  affiliation: |
    | Department of Mathematics and Statistics
    | Loyola University Chicago

@@

```{r child = "02-data.Rmd"}
```

```{r child = "03-methods.Rmd"}
```

```{r child = "04-results.Rmd"}
```

```{r child = "05-discussion.Rmd"}
```

### 2023-04-11 paper/04-results.Rmd
added more figures

Figure \ref{fig:fig_pos_curves} shows pos curves

@@

Fairly strong correlation (r = 0.6254943) between average STRAIN & hurries + sacks + hits per snaps

@@

From @Franks2016Meta (github https://github.com/afranks86/meta-analytics)

@@

@@

0.8544865

Figure \ref{fig:fig_stability} shows

Average STRAIN across all frames played in first and last 4 weeks

Strong correlation shows great metric stability

>>>>

```{r}
#| label: fig_outcome_curves
#| fig.cap: "STRAIN curves for different positions by outcome"
#| fig.width: 6
#| fig.height: 6
source(here("scripts", "08_fig_outcome_curves.R"))
fig_outcome_curves
```

Figure \ref{fig:fig_pos_curves} displays the average STRAIN by position for the first 40 frames (4 seconds) after the snap. We observe a clear difference in STRAIN between edge rushers (OLB's and DE's) and interior linemen (DT's and NT's). Specifically, edge rushers have higher STRAIN than interior linemen on average, as they are more easily able to approach the quarterback on the edge of the pocket versus, for instance, a nose tackle attacking the line head on.

On average, STRAIN appears to increase for the first 0.5 seconds of a play, followed by a decline in the next second. STRAIN then increases again until around 2.5-3 seconds after the snap before trending down towards the end of the play. In context, this reflects the actions that a pass-rusher initially moves towards the quarterback, but is then stopped by the offensive line while the quarterback drops back. When the quarterback stops dropping, the rusher closes the gap and increases STRAIN, before slowing down later on.

Further, Figure \ref{fig:fig_outcome_curves} shows the positional STRAIN curves by whether a play's outcome is a hit, sack, hurry, or none of those.

@@

@@

<!-- From @Franks2016Meta (github https://github.com/afranks86/meta-analytics) -->

@@

We observe a fairly strong correlation (r = 0.625) between average STRAIN and pressure rate.

@@

Figure \ref{fig:fig_stability} is a scatterplot of average STRAIN across all frames played in first and last 4 weeks.
It is apparent that there is a strong correlation (r = 0.854), illustrating great metric stability.

## Multilevel Model

coefficient table

icc
rusher 0.0574
blocker 0.0121
passer 0.0233
Residual 0.907

```{r}
#| label: fig_rankings_boot
#| fig.cap: "steve"
#| fig.width: 6
#| fig.height: 8
source(here("scripts", "10_multilevel_mod.R"))
fig_rankings_boot
```
